---
title: "HW6"
author: "Qi Qi"
date: "10/19/2018"
output: pdf_document
---

```{r setup, include=FALSE}
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 5.2.1
*
$$C\int_0^\infty(2x^{\theta-1}+x^{\theta-1/2})e^{-x}dx=2C\int_0^\infty x^{\theta-1}e^{-x}dx+C\int_0^\infty x^{\theta-1/2}e^{-x}dx$$
$$=2C\Gamma(\theta)\int_0^\infty \frac{x^{\theta-1}e^{-x}}{\Gamma(\theta)}dx+C\Gamma(\theta+1/2)\int_0^\infty \frac{x^{\theta-1/2}e^{-x}}{\Gamma(\theta+1/2)}dx$$
$$=2C\Gamma(\theta)+C\Gamma(\theta+1/2)=1 \Rightarrow C=\frac{1}{2\Gamma(\theta)+\Gamma(\theta+1/2)}$$
$$g(x)=\frac{2\Gamma(\theta)}{2\Gamma(\theta)+\Gamma(\theta+1/2)}x^{\theta-1}e^{-x}+\frac{\Gamma(\theta+1/2)}{\Gamma(\theta)+\Gamma(\theta+1/2)}x^{\theta-1/2}e^{-x}$$
Thus, $g$ is a mixture of $Gamma(\theta,1)$ and $Gamma(\theta+1/2, 1)$ with weight $\frac{2\Gamma(\theta)}{2\Gamma(\theta)+\Gamma(\theta+1/2)}$ and $\frac{\Gamma(\theta+1/2)}{2\Gamma(\theta)+\Gamma(\theta+1/2)}$.

*

Step 1: sample $U$ from $U(0,1)$.

Step 2: if $U<\frac{2\Gamma(\theta)}{2\Gamma(\theta)+\Gamma(\theta+1/2)}$ then sample $X$ from $Gamma(\theta,1)$; if $U \geq \frac{2\Gamma(\theta)}{2\Gamma(\theta)+\Gamma(\theta+1/2)}$ then sample $X$ from $Gamma(\theta+1/2,1)$.

Step 3: return $X$.

```{r}
rg <- function(theta, n){
  X <- NA
  for (i in 1:n){
    u <- runif(1,0,1)
    if (u < 2 * gamma(theta) / (2 * gamma(theta) + gamma(theta + 1/2))){
      X[i] <- rgamma(1, shape = theta, scale = 1)
    }else{
      X[i] <- rgamma(1, shape = theta + 1 / 2, scale = 1)
    }
  }
  return(X)
}

n <- 10000
theta1 <- 1
x1 <- rg(theta1, n)

dg <- function(x, theta){
  y <-2 * gamma(theta) / (2 * gamma(theta) + gamma(theta + 1/2)) * dgamma(x, shape = theta, scale = 1) + gamma(theta + 1/2) / (2 * gamma(theta) + gamma(theta + 1/2)) * dgamma(x, shape = theta + 1/2, scale = 1)
  return(y)
}

plot(density(x1), main = "theta=1")
curve(dg(x, theta1), add = TRUE, col = "red")


theta2 <- 2
x2 <- rg(theta2, n)

plot(density(x2), main = "theta=2")
curve(dg(x, theta2), add = TRUE, col = "red")
```

*

$$q(x)=\sqrt{4+x}x^{\theta-1}e^{-x}$$
$$\frac{q(x)}{g(x)}=\frac{\sqrt{4+x}}{C(2+\sqrt{x})}\leq \frac{2+\sqrt{x}}{C(2+\sqrt{x})}=\frac{1}{C}$$
So, we can let $\alpha=\frac{1}{C}$.
$$\frac{q(x)}{\alpha g(x)}=\frac{\sqrt{4+x}x^{\theta-1}e^{-x}}{(2x^{\theta-1}+x^{\theta-1/2})e^{-x}}=\frac{\sqrt{4+x}}{2+\sqrt{x}}$$

Step 1: sample $X \sim g$ and $U \sim U(0,1)$.

Step 2: if $U>\frac{q(x)}{\alpha g(x)}$, then go to step 1; else, return $X$.

```{r}
rf <- function(theta, n){
  y <- NA
  i <- 0
  while (i <= n){
     u <- runif(1, 0, 1)
     x <- rg(theta, 1)
     if (u <= sqrt(4 + x) / (2 + sqrt(x))){
       y[i] <- x
       i <- i + 1
     }
  }
 return(y)
}


theta1 <- 1
x1 <- rf(theta1, 10000)
plot(density(x1), main = "theta=1")

theta2 <- 2
x2 <- rf(theta2, 10000)
plot(density(x2), main = "theta=2")
```

# Exercise 5.2.2
*

$$g_1(x)=\frac{x^{\theta-1}}{Beta(\theta, 1)}=\frac{x^{\theta-1}}{\theta}$$
$$g_2(x)=\frac{(1-x)^{\beta-1}}{Beta(1, \beta)}=\frac{(1-x)^{\beta-1}}{\beta}$$
$$p_1=\frac{\theta}{\theta+\beta}, \ p_2=\frac{\beta}{\theta+\beta}$$
Then, $$g(x)=\frac{x^{\theta-1}+(1-x)^{\beta-1}}{\theta+\beta}$$
$$\frac{q(x)}{g(x)}=\frac{\frac{x^{\theta-1}}{1+x^2}+\sqrt{2+x^2}(1-x)^{\beta-1}}{\frac{x^{\theta-1}+(1-x)^{\beta-1}}{\theta+\beta}}$$
$$\leq \frac{\frac{x^{\theta-1}}{1+x^2}+\frac{(1-x)^{\beta-1}}{1+x^2}}{\frac{x^{\theta-1}+(1-x)^{\beta-1}}{\theta+\beta}}=\frac{\theta+\beta}{1+x^2}\leq \theta+\beta$$

Let $\alpha=\theta+\beta$, 
$$\frac{q(x)}{\alpha g(x)}=\frac{\frac{x^{\theta-1}}{1+x^2}+\sqrt{2+x^2}(1-x)^{\beta-1}}{x^{\theta-1}+(1-x)^{\beta-1}}$$

Step 1: sample $X \sim g$ and $U \sim U(0,1)$.

Step 2: if $U>\frac{q(x)}{\alpha g(x)}$, then go to step 1; else, return $X$.

```{r}
rg <- function(theta, beta, n){
  X <- NA
  for (i in 1:n){
    u <- runif(1,0,1)
    if (u < theta / (theta + beta)){
      X[i] <- rbeta(1, shape1 = theta, shape2 = 1)
    }else{
      X[i] <- rbeta(1, shape1 = 1, shape2 = beta)
    }
  }
  return(X)
}

rf <- function(theta, beta, n){
  y <- NA
  i <- 0
  while (i <= n){
     u <- runif(1, 0, 1)
     x <- rg(theta, beta, 1)
     if (u <= (x ^ (theta - 1) / (1 + x ^ 2) + sqrt(2 + x ^ 2) * (1 - x) ^ (beta - 1)) / (x ^ (theta - 1) + (1 - x) ^ (beta - 1))){
       y[i] <- x
       i <- i + 1
     }
  }
 return(y)
}

theta1  <- 1
beta1 <- 2
x1 <- rf(theta1, beta1, 10000)
plot(density(x1), main = "theta=1, beta=2")

theta2  <- 2
beta2 <- 1
x2 <- rf(theta2, beta2, 10000)
plot(density(x2), main = "theta=2, beta=1")
```

*

$$q_1(x)=\frac{x^{\theta-1}}{1+x^2}$$
$$g_1(x)=\frac{x^{\theta-1}}{Beta(\theta, 1)}=\frac{x^{\theta-1}}{\theta}$$
$$\frac{q_1(x)}{g_1(x)}=\frac{\theta}{1+x^2}\leq \theta=\alpha_1$$
$$\frac{q_1(x)}{\alpha_1g_1(x)}=\frac{1}{1+x^2}$$
$$q_2(x)=\sqrt{2+x^2}(1-x)^{\beta-1}$$
$$g_2(x)=\frac{(1-x)^{\beta-1}}{Beta(1, \beta)}=\frac{(1-x)^{\beta-1}}{\beta}$$
$$\frac{q_2(x)}{g_2(x)}=\beta \sqrt{2+x^2} \leq \beta \sqrt{3}=\alpha_2$$
$$\frac{q_2(x)}{\alpha_2g_2(x)}=\sqrt{\frac{2+x^2}{3}}$$
Step 1: sample $k$ from $\{1,2\}$ with probability $\frac{\theta}{\theta+\beta\sqrt{3}}$ and $\frac{\beta\sqrt{3}}{\theta+\beta\sqrt{3}}$.

Step 2: sample $X \sim g_k$ and $U \sim U(0,1)$

Step 3: if $U > \frac{q_k(x)}{\alpha_kg_k(x)}$ then go to step 1; else, return $X$.

```{r}
rf <- function(theta, beta, n){
  i <- 0
  y <- NA
  while (i <= n){
    p <- runif(1, 0, 1)
    if (p < theta / (theta + beta * sqrt(3))){
      u <- runif(1, 0, 1)
      x <- rbeta(1, shape1 = theta, shape2 = 1)
      if (u <= 1 / (1 + x ^ 2)){
        y[i] <- x
        i <- i + 1
      }
    }else{
      u <- runif(1, 0, 1)
      x <- rbeta(1, shape1 = 1, shape2 = beta)
      if (u <= sqrt( (2 + x ^ 2) / 3)) {
        y[i] <- x
        i <- i + 1
      }
    }
  }
  return (y)
}

theta1  <- 1
beta1 <- 2
x1 <- rf(theta1, beta1, 10000)
plot(density(x1), main = "theta=1, beta=2")

theta2  <- 2
beta2 <- 1
x2 <- rf(theta2, beta2, 10000)
plot(density(x2), main = "theta=2, beta=1")
```